\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2014-10-02 paper2015asml.tex
more fixes

\begin{table*}[t]
\centering
\scalebox{0.9}{
\begin{tabular}{|c||c|c|c|c|c|c|c|}
\hline
Efficiency  & Highly inefficient& Moderately inefficient& Slightly inefficient& Neutral & Slightly efficient& Moderately efficient& Highly efficient\\
\hline
Elegance    & Highly awkward& Moderately awkward& Slightly awkward& Neutral & Slightly elegant& Moderately elegant& Highly elegant\\
\hline
Smoothness  & Highly rough& Moderately rough& Slightly rough& Neutral & Slightly smooth& Moderately smooth& Highly smooth\\
\hline
Overall     & Extremely poor& Moderately poor& Somewhat poor& Neutral & Somewhat good& Moderately good& Extremely good\\
\hline
\end{tabular}
}
\caption{The rating categories and the associated scale presented to the survey respondent}
\label{tab:rating_scales}
\end{table*}

@@

We conducted an online survey\footnote{The online survey was conducted after gaining a waiver from SRI's IRB after a review of our survey procedure. Our survey followed standard guidelines for privacy of respondent information when conducting a survey on Mechanical Turk.} where we asked human observers to rate a variety of trajectories of the PR2 robot. The survey was built on Amazon's Mechanical Turk~\cite{paolacci2010running}, which has become a useful tool for large online data gathering and crowd-sourced work. Each respondent in the survey was presented with a set of demographic questions, a video, and four scales to rate the robot's motion on the attributes  of elegance, efficency, smoothness and overall impression (a summary of the rating scales used in the main survey question can be seen in Table~\ref{tab:rating_scales}). Each respondent was expected to rate multiple trajectories but could not rate a trajectory more than once. Each video has four different views of the robot displayed simultaneously. Respondents were asked demographic questions about familiarity with video games, familiarity with robotics, age group and highest education level. The demographic information was not used to filter the responses we collected.

@@

\section{Survey Results and Analysis}
\label{sec:raw_results}
The survey resulted in at least 20 ratings for each trajectory (so there were a total of 2060 ratings from participants in the survey). In this section, we will first analyze the raw results from the survey (which are interesting in themselves). Subsequently, we will present a set of features that were used to represent individual trajectories. These features will be used in the next section to learn the human-observer ratings for robot trajectories. 
\subsection{Raw Survey Results}
\begin{figure}[h]
  \centering{\includegraphics[width=0.45\linewidth]{pictures/efficiency}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/elegant}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/smooth}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/overall}}
  \caption{Histogram of averaged ratings for the 103 different trajectories. Clockwise from top left: Efficient vs. Inefficient, Elegant vs. Inelegant, Smooth vs. Rough, Overall Rating}
\label{fig:survey_raw}
\end{figure}
The raw results of the survey are summarized in Fig.~\ref{fig:survey_raw} which shows a histogram of averaged responses for each of the four survey questions across the 103 trajectories that were rated by users. It is clear that a majority of the trajectories in our survey were well received by the human observers but there were quite a few trajectories that were rated badly as well. An analysis of the ratings for each trajectory showed that four (averaged) ratings for each individual trajectory were always similar to each other, indicating that users had similar preferences for each trajectory regardless of the individual attributes used to describe the preference for the trajectory (efficient, elegant, smooth, overall). Table~\ref{tab:correlation} shows the Pearson's correlation coefficients corresponding to pairs of attributes. Attributes across individual questions are highly correlated at a statistically significant level of 1\% (with p-values $< 0.01\%$). Confidence intervals for the overall rating of each trajectory are shown in Fig.~\ref{confidence}. The small spread in the confidence intervals clearly indicates that different users had similar opinions about the same trajectory.

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline
& Efficient & Elegant & Smooth & Overall \\ \hline
Efficient & 1 & 0.96 & 0.91 & 0.98 \\ \hline
Elegant & 0.96 & 1 & 0.96 & 0.98 \\ \hline
Smooth & 0.91 & 0.96 & 1 & 0.96 \\ \hline
Overall & 0.98 & 0.98 & 0.96 & 1 \\ \hline
\end{tabular}
\caption{Correlation between the four attributes in the survey.}
\label{tab:correlation}
\end{table}

@@

The first set of features we compute for each trajectory take into account the environment around the robot, the shape of the trajectory and the dynamics of the trajectory. These make up our unary features computed only on the input trajectory. We also include features that compare each trajectory to a nominal trajectory - these feature serve to characterize how much the trajectory deviates from the "expected" path. We go over the multi-point features in the next section. First, we detail the features we computed on each trajectory \tj{} with waypoints $q_i$ where $i={0,\mathellipsis,n}$ and $n=|\tj{}|$. Note that our features are generic, i.e. they can be computed in the same manner for any robot arm trajectory. We believe that our methods should be easily extensible to robots other than the PR2 as well and individual trajectory classifiers could be built for each different robot arm in a similar manner.

@@

\subsection{Multi-Trajectory Features}
\label{subsec:multi_traj_feat}
We also wanted to design features that captured the difference between the planned trajectory and an expected path for the end-effector in the environment. The expected or nominal end-effector trajectories were created using a breadth-first search in a 3D voxel approximation of the planning problem. The environment model was first discretized into a voxel-grid, and voxels are marked as occupied or empty. Any voxel that is partially occupied is considered to be occupied. A 26-connected grid was used in the planning process to find a path in the voxel grid for a cubical shape moving from the start position of the end-effector of the arm to the desired goal position.  Essentially, this would be the optimal path followed by the end-effector from start to goal if it were modeled as a free-standing cube. Next, we compute comparison features between $\xi_{\text{BFS}}$ and three workspace trajectories for the elbow ($\xi_\text{elbow}$), wrist ($\xi_\text{wrist}$) and finger-tip ($\xi_\text{tip}$) links. The comparison features computed between each pair of trajectories are the Hausdorff distances~\cite{dubuisson1994modified} and Dynamic Time Warping~\cite{senin2008dynamic} distances.

@@

\begin{table}
\label{tab:feature_description}
\scalebox{0.9}{
\centering
\begin{tabular}{|p{0.3\columnwidth}|p{0.2\columnwidth}|p{0.5\columnwidth}|}
\hline
Feature Name & Metric & Feature Description \\
\hline
path\_length, smoothness, clearance, max\_lin\_acc, joint\_limit\_distance & Joint-space & Features discussed in Section~\ref{subsec:traj_feat} computed on joint-space trajectory \tj{}\\
\hline
[link]\_length, [link]\_smoothness, [link]\_max\_curvature, [link]\_lin\_acc, [link]\_quat\_dist & Cartesian & Features discussed in Section~\ref{subsec:traj_feat} computed on 3D cartesian path traced by [link] in \tj{}\\
\hline
h\_[link]\_bfs, h\_[link1]\_[link2], H\_[link]\_bfs, H\_[link1]\_[link2] & Cartesian & Assymetric ($h$) or symmetric ($H$) hausdorff distance between 3D cartesian path traced by [link] in \tj{} w.r.t BFS path or between 3D Cartesian path traced by [link1] and [link2] in \tj{}\\
\hline
[link]\_bfs\_dtw, [link1]\_[link2]\_dtw & Cartesian & DTW cost between path traced by [link] in \tj{} and the BFS path, or between 3D-cartesian-path traced by [link1] and [link2] in \tj{}\\
\hline
\end{tabular}
}
\caption{Decoding of feature names into descriptions}
\end{table}

@@

\begin{figure}[t]
  \centering{\includegraphics[width=0.90\linewidth]{pictures/meandecrease}}
  \caption{Random Forest: Mean decrease in accuracy for each feature.}
\label{fig:feature_importance_1}
\end{figure}

\begin{figure}[t]
 \centering{\includegraphics[width=0.90\linewidth]{pictures/gini}}
  \caption{Random Forest: Gini index (higher values indicate more important features).}
\label{fig:feature_importance_2}
\end{figure}

\begin{figure}[t]
 \centering{\includegraphics[width=0.90\linewidth]{pictures/gini}}
  \caption{Boosting: Gini index (higher values indicate more important features).}
\label{fig:gini_boosting}
\end{figure}

@@

\section{Conclusion}
In this work, we have generated ratings for a large dataset of robot trajectories. We have already gained significant insights into the 
types of trajectories that are preferred by human observers. In particular, we have been able to identify a set of features that seem to influence 
the human's perception of the trajectories the most. This can help us in defining better cost functions when generating the trajectories. The classifiers 
that we have learned could also be used to directly inform gradient free motion planning algorithms by assigning a rating to new trajectories. Our 
results were generated using a single robot model (the PR2) but we believe that they will easily translation to other robot models as well. To this end, 
we will keep the survey open and attempt to collect data for a larger set of trajectories in 
more environments and with different robots.

>>>>

\begin{table*}[t]
\centering
\scalebox{0.9}{
\begin{tabular}{|c||c|c|c|c|c|c|c|}
\hline
Efficiency  & Highly inefficient& Moderately inefficient& Slightly inefficient& Neutral & Slightly efficient& Moderately efficient& Highly efficient\\
\hline
Elegance    & Highly awkward& Moderately awkward& Slightly awkward& Neutral & Slightly elegant& Moderately elegant& Highly elegant\\
\hline
Smoothness  & Highly rough& Moderately rough& Slightly rough& Neutral & Slightly smooth& Moderately smooth& Highly smooth\\
\hline
Overall     & Extremely poor& Moderately poor& Somewhat poor& Neutral & Somewhat good& Moderately good& Extremely good\\
\hline
\end{tabular}
}
\caption{The four rating categories/attributes and the associated scales for each presented to the survey respondent.}
\label{tab:rating_scales}
\end{table*}

@@

We conducted an online survey\footnote{The online survey was conducted after gaining a waiver from SRI's IRB after a review of our survey procedure. Our survey followed standard guidelines for privacy of respondent information when conducting a survey on Mechanical Turk.} where we asked human observers to rate a variety of trajectories of the PR2 robot. The survey was built on Amazon's Mechanical Turk~\cite{paolacci2010running}, which has become a useful tool for large online data gathering and crowd-sourced work. Each respondent in the survey was presented with a set of demographic questions, a video, and asked to rate the robot's motion on the attributes  of elegance, efficency, smoothness and overall impression (a summary of the rating scales used in the main survey question can be seen in Table~\ref{tab:rating_scales}). The ratings were later converted into numerical values on a scale of 1 to 7. Each respondent was expected to rate multiple trajectories but could not rate a trajectory more than once. Each video has four different views of the robot displayed simultaneously. Respondents were asked demographic questions about familiarity with video games, familiarity with robotics, age group and highest education level. The demographic information was not used to filter the responses we collected.

@@

\section{Survey Results and Analysis}
\label{sec:raw_results}
The survey resulted in at least 20 ratings for each trajectory (so there were a total of 2060 ratings from participants in the survey). In this section, we will first analyze the raw results from the survey (which are interesting in themselves). Subsequently, we will present a set of features that were used to represent individual trajectories. These features will be used in the next section to learn the human-observer ratings for robot trajectories. 
\subsection{Raw Survey Results}
\begin{figure}[h]
  \centering{\includegraphics[width=0.45\linewidth]{pictures/efficiency}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/elegant}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/smooth}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/overall}}
  \caption{Histogram of averaged ratings for the 103 different trajectories. Clockwise from top left: Efficient vs. Inefficient, Elegant vs. Inelegant, Smooth vs. Rough, Overall Rating}
\label{fig:survey_raw}
\end{figure}
The raw results of the survey are summarized in Fig.~\ref{fig:survey_raw} which shows a histogram of averaged responses for each of the four survey questions across the 103 trajectories that were rated by users. It is clear that a majority of the trajectories in our survey were well received by the human observers but there were quite a few trajectories that were rated badly as well. An analysis of the ratings for each trajectory showed that four (averaged) ratings for each individual trajectory were always similar to each other, indicating that users had similar preferences for each trajectory regardless of the individual attributes used to describe the preference for the trajectory (efficient, elegant, smooth, overall). Table~\ref{tab:correlation} shows the Pearson's correlation coefficients corresponding to pairs of attributes. Attributes across individual questions are highly correlated at a statistically significant level of 1\% (with p-values $< 0.01\%$). The 95\% confidence intervals for all the four ratings for each trajectory was less than 1.0. 
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline
& Efficient & Elegant & Smooth & Overall \\ \hline
Efficient & 1 & 0.96 & 0.91 & 0.98 \\ \hline
Elegant & 0.96 & 1 & 0.96 & 0.98 \\ \hline
Smooth & 0.91 & 0.96 & 1 & 0.96 \\ \hline
Overall & 0.98 & 0.98 & 0.96 & 1 \\ \hline
\end{tabular}
\caption{Correlation between the four attributes in the survey.}
\label{tab:correlation}
\end{table}

@@

We identified and computed multiple types of trajectory features. The first set of features we compute for each trajectory take into account the environment around the robot, the shape of the trajectory and the dynamics of the trajectory. These make up our unary features computed only on the input trajectory. We also include features that compare each trajectory to a nominal trajectory - these feature serve to characterize how much the trajectory deviates from the "expected" path. We go over the multi-point features in the next section. First, we detail the features we computed on each trajectory \tj{} with waypoints $q_i$ where $i={0,\mathellipsis,n}$ and $n=|\tj{}|$. Note that our features are generic, i.e. they can be computed in the same manner for any robot arm trajectory. We believe that our methods should be easily extensible to robots other than the PR2 as well and individual trajectory classifiers could be built for each different robot arm in a similar manner.

@@

\subsection{Comparative Trajectory Features}
\label{subsec:multi_traj_feat}
We also wanted to design features that captured the difference between the planned trajectory and an expected path for the end-effector in the environment. The expected or nominal end-effector trajectories were created using a breadth-first search in a 3D voxel approximation of the planning problem. The environment model was first discretized into a voxel-grid, and voxels are marked as occupied or empty. Any voxel that is partially occupied is considered to be occupied. A 26-connected grid was used in the planning process to find a path in the voxel grid for a cubical shape moving from the start position of the end-effector of the arm to the desired goal position.  Essentially, this would be the optimal path followed by the end-effector from start to goal if it were modeled as a free-standing cube. Next, we compute comparison features between $\xi_{\text{BFS}}$ and three workspace trajectories for the elbow ($\xi_\text{elbow}$), wrist ($\xi_\text{wrist}$) and finger-tip ($\xi_\text{tip}$) links. The comparison features computed between each pair of trajectories are the Hausdorff distances~\cite{dubuisson1994modified} and Dynamic Time Warping~\cite{senin2008dynamic} distances.

@@

\begin{table}
\label{tab:feature_description}
\scalebox{0.9}{
\centering
\begin{tabular}{|p{0.3\columnwidth}|p{0.2\columnwidth}|p{0.5\columnwidth}|}
\hline
Feature Name & Metric & Feature Description \\
\hline
path\_length, smoothness, clearance, max\_lin\_acc, joint\_limit\_distance & Joint-space & Features discussed in Section~\ref{subsec:traj_feat} computed on joint-space trajectory \tj{}\\
\hline
[link]\_length, [link]\_smoothness, [link]\_max\_curvature, [link]\_lin\_acc, [link]\_quat\_dist & Cartesian & Features discussed in Section~\ref{subsec:traj_feat} computed on 3D cartesian path traced by [link] in \tj{}\\
\hline
h\_[link]\_bfs, h\_[link1]\_[link2], H\_[link]\_bfs, H\_[link1]\_[link2] & Cartesian & Assymetric ($h$) or symmetric ($H$) hausdorff distance between 3D cartesian path traced by [link] in \tj{} w.r.t BFS path or between 3D Cartesian path traced by [link1] and [link2] in \tj{}\\
\hline
[link]\_bfs\_dtw, [link1]\_[link2]\_dtw & Cartesian & DTW cost between path traced by [link] in \tj{} and the BFS path, or between 3D-cartesian-path traced by [link1] and [link2] in \tj{}\\
\hline
\end{tabular}
}
\caption{The complete list of computed trajectory features used for classification.}
\end{table}

@@

\begin{figure}[t]
  \centering{\includegraphics[width=0.90\linewidth]{pictures/meandecrease}}
  \caption{Random Forest: Mean decrease in accuracy for each feature.}
\label{fig:feature_importance_1}
\vspace{-0.2in}
\end{figure}
\begin{figure}[t]
 \centering{\includegraphics[width=0.90\linewidth]{pictures/gini}}
  \caption{Random Forest: Gini index (higher values indicate more important features).}
\label{fig:feature_importance_2}
\vspace{-0.3in} 
\end{figure}
\begin{figure}[t]
 \centering{\includegraphics[width=0.90\linewidth]{pictures/gini}}
  \caption{Boosting: Gini index (higher values indicate more important features).}
\label{fig:gini_boosting}
\vspace{-0.3in}
\end{figure}

@@

\section{Conclusion}
\label{sec:conclusion}
In this work, we have generated ratings for a large dataset of robot trajectories. We have already gained significant insights into the 
types of trajectories that are preferred by human observers. In particular, we have been able to identify a set of features that seem to influence 
the human's perception of the trajectories the most. This can help us in defining better cost functions when generating the trajectories. The classifiers 
that we have learned could also be used to directly inform gradient free motion planning algorithms by assigning a rating to new trajectories. Our 
results were generated using a single robot model (the PR2) but we believe that they will easily translation to other robot models as well. To this end, 
we will keep the survey open and attempt to collect data for a larger set of trajectories in 
more environments and with different robots.
